**The status of the microbial census: an update**

### 2015-12-04 doc/notebook/Archaeal_data_acquisition.Rmd
Add emirge metadata; fix output of rarefaction to data/process

XXXXXXXXXXXXXXXX

@@

@@

```{r, engine="bash"}
mothur "#set.dir(input=data/mothur, output=data/mothur);
        make.shared(list=all_archaea.filter.unique.precluster.an.list, group=archaea.all_category.groups, label=unique-0.03-0.05-0.10-0.20);
        system(mv data/mothur/all_archaea.filter.unique.precluster.an.shared data/mothur/all_archaea.all_categories.shared);
        rarefaction.single(shared=all_archaea.all_categories.shared);
        summary.single(shared=all_archaea.all_categories.shared, calc=nseqs-sobs-coverage)"

mothur "#set.dir(input=data/mothur, output=data/mothur);
        make.shared(list=all_archaea.filter.unique.precluster.an.list, group=archaea.pool_category.groups, label=unique-0.03-0.05-0.10-0.20);
        system(mv data/mothur/all_archaea.filter.unique.precluster.an.shared data/mothur/all_archaea.pool_category.shared);
        rarefaction.single(shared=all_archaea.pool_category.shared);
        summary.single(shared=all_archaea.pool_category.shared, calc=nseqs-sobs-coverage)"

mothur "#set.dir(input=data/mothur, output=data/mothur);
        make.shared(list=all_archaea.filter.unique.precluster.an.list, group=archaea.env_category.groups, label=unique-0.03-0.05-0.10-0.20);
        system(mv data/mothur/all_archaea.filter.unique.precluster.an.shared data/mothur/all_archaea.env_category.shared);
        rarefaction.single(shared=all_archaea.env_category.shared);
        summary.single(shared=all_archaea.env_category.shared, calc=nseqs-sobs-coverage)"

mothur "#rarefaction.single(list=data/mothur/all_archaea.filter.unique.precluster.an.list, label=unique-0.03-0.05-0.10-0.20);"
```

>>>>

@@

We'd also like to get the metadata from the EMIRGE data. We have an metadata file was created above with `code/get_emirge.metadata.sh` that we'll read in and concatenate to the end of `archaea.good.metadata`.

```{r emirge_metadata}
emirge_metadata <- read.table(file="data/raw/emirge.metadata", row.names=1)
archaea_sequences <- read.table(file="data/mothur/emirge.archaea.taxonomy")[1]
archaea_emirge_metadata <- emirge_metadata[archaea_sequences$V1,]

write.table(archaea_emirge_metadata, file="data/mothur/archaea.good.metadata", quote=TRUE, sep="\t", col.names=F, append=T)
```

@@

```{r, engine="bash"}
mothur "#set.dir(input=data/mothur, output=data/mothur);
        make.shared(list=all_archaea.filter.unique.precluster.an.list, group=archaea.all_category.groups, label=unique-0.03-0.05-0.10-0.20);
        system(mv data/mothur/all_archaea.filter.unique.precluster.an.shared data/mothur/all_archaea.all_categories.shared);
        rarefaction.single(shared=all_archaea.all_categories.shared, outputdir=data/process)"

mothur "#set.dir(input=data/mothur, output=data/mothur);
        make.shared(list=all_archaea.filter.unique.precluster.an.list, group=archaea.pool_category.groups, label=unique-0.03-0.05-0.10-0.20);
        system(mv data/mothur/all_archaea.filter.unique.precluster.an.shared data/mothur/all_archaea.pool_category.shared);
        rarefaction.single(shared=all_archaea.pool_category.shared, outputdir=data/process)"

mothur "#set.dir(input=data/mothur, output=data/mothur);
        make.shared(list=all_archaea.filter.unique.precluster.an.list, group=archaea.env_category.groups, label=unique-0.03-0.05-0.10-0.20);
        system(mv data/mothur/all_archaea.filter.unique.precluster.an.shared data/mothur/all_archaea.env_category.shared);
        rarefaction.single(shared=all_archaea.env_category.shared, outputdir=data/process)"

mothur "#rarefaction.single(list=data/mothur/all_archaea.filter.unique.precluster.an.list, label=unique-0.03-0.05-0.10-0.20, outputdir=data/process);"

rm data/mothur/*rabund data/mothur/mothur*logfile mothur*logfile
```
